### 2022-11-14 NSF2022/Description/summary.tex
edited SA1

\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective dynamics of amphiphilic particles. The simulations use a new, yet intuitive, approach that accounts for important and complex systems that are presently out of reach in computational material science. These complex systems include optimal shape design in metamaterials and fusion and fission of amphiphilic bilayer membranes. The models describing colloidal systems could be transformative in biomedicine and material science. The research draws from expertise in scientific computing, physics of fluids, and mathematics. The mathematical component incorporates leading variational techniques and offers insight into fundamentals of material science. The project brings socially consequential research into the classroom and offers undergraduates the opportunity to train alongside faculty and graduate students. With its combination of mathematical modeling, analysis, and scientific computing, the project highlights the importance of mathematics and computation to all areas of science and engineering.
\end{document}

>>>>

\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates leading variational techniques and
offers insight into fundamentals of self-organization and collective
dynamics. The project brings socially consequential research into the
classroom and offers undergraduates the opportunity to train alongside
faculty and graduate students. With its unique combination of
mathematical modeling, analysis, and scientific computing, the project
highlights the potential advancement of STEM from applied mathematics.

\end{document}
